Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-03-07 Master Thesis/synopsis.tex
Update corollary-fkschmidt

\begin{proof}
Let $L$ be the fixed field of $G_{w_1}\cap G_{w_2}$ and set $v_i = w_i|_L$. Then $L$ is henselian with respect to both $v_1$ and $v_2$. Since $v_1$ and $v_2$ are unramified in $K^\text{s}/L$, they are inequivalent valuations of rank $1$. Now $L$ is separably closed by Theorem \ref{theorem-fkschmidt}. Therefore by Theorem \ref{theorem-henselization} we get $G_{{w_1}}\cap G_{{w_1}}=G_L =1$.
\end{proof}

>>>>

\begin{proof}
Let $L$ be the fixed field of $G_{w_1}\cap G_{w_2}\subset G_K$ and set $v_i = w_i|_L$. Then $L$ is henselian with respect to both $v_1$ and $v_2$. Since $w_1,w_2$ are the only extensions of $v_1$ and $v_2$ in $K^\text{s}$ respectively, $v_1$ and $v_2$ are inequivalent valuations of rank $1$. Now $L$ is separably closed by Theorem \ref{theorem-fkschmidt}. Therefore by Theorem \ref{theorem-henselization} we get $G_{{w_1}}\cap G_{{w_1}}=G_L =1$.
\end{proof}
